Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-08-12 Rdocs/ManuscriptLPP.Rmd
Finalized changes to scripts for publication

```{r pre-requisite scripts, echo=FALSE}
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/statistics.R") #script to analyze previously loaded data
source("Rscripts/plot_source.R") #source code for custom plotting functions

>>>>

```{r pre-requisite scripts, echo=FALSE}
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/stats.R") #script to analyze previously loaded data
source("Rscripts/plot_source.R") #source code for custom plotting functions
